MRD_final_microbiome

### 2019-06-18 GlobalMicrobiome_NS.Rmd
updated

p1 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "mnd")
plot(p1 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + labs(color = "MND Prevalence"))
ggsave("NMDSt.png")

p1 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~mnd, nrow = 2) + labs(color = "MND Prevalence")
ggsave("NMDS_facet.png")

@@

>>>>

p1 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "mnd")
plot(p1 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + labs(color = "MND Prevalence"))
ggsave("NMDStMND.png")

p1 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~mnd, nrow = 2) + labs(color = "MND Prevalence")
ggsave("NMDS_facetMND.png")

p2 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "pd")
plot(p2 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + labs(color = "PD Prevalence"))
ggsave("NMDStpd.png")

p2 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~mnd, nrow = 2) + labs(color = "PD Prevalence")
ggsave("NMDS_facetpd.png")

p3 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "pd")
plot(p3 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + labs(color = "PD Prevalence"))
ggsave("NMDStpd.png")

p3 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~mnd, nrow = 2) + labs(color = "PD Prevalence")
ggsave("NMDS_facetpd.png")

@@

p2 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "pd")
plot(p2 + scale_colour_manual(values = c( "yellow", "orange", "red", "grey")) + labs(color = "PD Prevalence"))
ggsave("MDSpd.png")

p2 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~pd, 3) + labs(color = "PD Prevalence")
ggsave("NMDS_facetPD.png")

p3 = plot_ordination(pseq.rel, pseq.ord, type = "sample", color = "ad")
plot(p3 + scale_colour_manual(values = c( "yellow", "orange", "red", "grey")) + labs(color = "AD Prevalence"))
ggsave("MDSad.png")

p3 + scale_colour_manual(values = c("yellow", "orange", "red", "grey")) + facet_wrap(~pd, 3) + labs(color = "AD Prevalence")
ggsave("NMDS_facetAD.png")
